Fourmile state variables

### 2025-03-13 state_vars.Rmd
starting anova for water partition
looking at high and low HRUs

# High elevation HRU

@@

statn_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_statn.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_grid.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

@@

# Low elevation HRU

@@

>>>>

# High elevation HRU - old

@@

statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  dplyr::select(-time)

grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  dplyr::select(-time)

@@

# Low elevation HRU - old

@@

# 2015 for low and high HRU

statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  dplyr::select(-time)

grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  dplyr::select(-time)

both_hi <- bind_rows(statn_hi, grid_hi) %>%
  mutate(year = year(date),
         month = month(date)) %>%
  filter(year == 2015,
         month %in% c(4,5,6))

swe <- ggplot(both_hi, 
               aes(date, 
                   snowTotSWE,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

ggplotly(swe)

statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  dplyr::select(-time)

grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  dplyr::select(-time)

both_hi <- bind_rows(statn_hi, grid_hi) %>%
  mutate(year = year(date),
         month = month(date)) %>%
  filter(year == 2015,
         month %in% c(4,5,6))

swe <- ggplot(both_hi, 
               aes(date, 
                   snowTotSWE,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

ggplotly(swe)

# ANOVA for water partition

flow <- both %>%
  select(date, 
         source, 
         outRG1,
         outRG2,
         outRD1, 
         outRD2,
         source)

rd1_model <- aov(outRD2 ~ source, data = flow)
summary(rd1_model)
